XOR-Some Prolific Pilot 2

### 2021-05-04 analysis/xor-some-prolific-pilot2.Rmd
minor fix

d_test_fail_zScore <- d_test_fail_zScore %>% 
  filter(passed_filler == F)
```

>>>>

d_test_fail_zScore <- d_test_fail_zScore %>% 
  ungroup() %>%
  filter(passed_filler == F)

cat(" Subjects failing the comprehension trials when using z-scored raw data: ", d_test_fail_zScore %>% distinct(submission_id) %>% pull() %>% length())
